### 2013-09-18 manuscripts/reply/reply.tex
More work on reply.

\section*{EB}
\citet{Hickerson2013} repeatedly refer the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.
However, this is bit misleading, as \citet{Oaks2012} discuss in detail how the
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail how the being limited to uniform prior distributions necessitates
awkward broad priors to avoid excluding the truth, a priori.
What \citet{Hickerson2013} really mean to say is that \citet{Oaks2012} did not
use an empirical Bayesian approach, which is what they do and advocate.

>>>>

\section*{EB}
\citet{Hickerson2013} repeatedly refer the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.
However, this is bit misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail how the being limited to uniform prior distributions necessitates
awkward broad priors to avoid excluding the truth, a priori.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did also use empirically informed priors when assessing
both the prior sensitivity of the method and determining the power of \msb
under the ``best'' possible real-world conditions.
\citet{Oaks2012} discuss the potential dangers of taking an empirical Bayesian
model choice (see last paragraph of ``Assessing prior sensitivity of \msb''),
and we expand on this here.

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a rational method of inductive learning in which Bayes'
rule is used to update our beliefs about a model as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \subset
\allParameterValues$ such that $p(\theta)$ describes our belief that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \subset
\allParameterValues$ and $\alignment{}{} \subset \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
        \myTheta{})p(\myTheta{})}{p(\alignment{i}{}},
    \label{eq:bayesrule}
\end{equation}
where $p(\alignment{i}{}) = \int{\myTheta{}} p(\alignment{i}{} \given
\myTheta{})p(\myTheta{}) d\myTheta{}$.
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

This is an elegant method of updating our beliefs as data are accumulated.
However, this all hinges on the fact that the prior ($p(\myTheta{})$) is
defined for all possible parameters independently of the new data being
analyzed.
Any other datasets or external information can safely be used to inform our
beliefs about $p(\myTheta{})$.
However, if the data are used to both inform the prior and calculate the
posterior, the prior becomes conditional on the data, and Bayes' rule breaks
down.

Now, this is not to say that empirical Bayesian approaches not useful.
Quite the contrary.
Empirical Bayes is a well studied branch of Bayesian statistics that
has given rise to a many powerful inference methods.
It is true that empirical Bayes methods have an uncertain theoretical basis and
do not yield a valid posterior distribution from Bayes' rule \citp[e.g.,
empirical Bayesian estimates of the posterior are often too narrow, off-center,
and misshapen;][]{Morris1983,Laird1987,Carlin1990,Efron2013}.
Nevertheless, empirical Bayes methods are often a powerful means of parameter
estimation that display favorable frequentist properties.
Furthermore, many post-hoc correction methods have been developed for
estimating confidence-intervals from empirical Bayes estimates of posterior
distributions that often display good frequentist coverage behavior
\citep{Morris1983,Laird1987,Laird1989, Carlin1990,Hwang2009}.

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is much more dubious.
In Bayesian model choice, the goal is usually not to estimate parameters, but
to estimate the relative probabilities of candidate models.
Unlike parameter estimates, posterior probabilities represent a summary of the
entire posterior distribution.
Thus, given that empirical Bayesian posterior distributions are not accurate,
there is no guarantee regarding the accuracy of probabilities summarized from
them.
